### 2021-10-12 docs/paper/sections/5_evaluation.tex
Try to shorten paper just a little bit more

To answer \cref{q2,q3} without our tool, users need to scan each found dependency separately to count or read all usage samples.
If they are intending to analyze the usage of a member with an unambiguous name, they can perform an expeditious string search.
This is possible using Sourcegraph or another search engine if the dependency is indexed there; otherwise, users will need to download the repository and search it locally.
If the member of interest has an ambiguous name, users will need to download the project and view it in an IDE such as VS Code that supports reference search.
Alternatively, they can try the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}); however, this feature is available for a small number of repositories only.

>>>>

To answer \cref{q2,q3} without our tool, users need to scan each found dependency separately to count or read all usage samples.
If they are intending to analyze the usage of a member with an unambiguous name, they can perform an expeditious string search.
This is possible using Sourcegraph or another search engine if the dependency is indexed there; otherwise, users will need to download the repository and search it locally.
If the member of interest has an ambiguous name, users will need to download the project and view it in an IDE such as VS Code that supports reference search.
Alternatively, they can try the precise code intelligence mode on Sourcegraph (see \cref{sec:related_work/usage_samples}); however, this feature is available for few repositories only.

### 2021-10-12 docs/paper/sections/6_conclusion.tex
Try to shorten paper just a little bit more

Downstream dependencies provide a promising perspective for package developers that are interested in understanding how their interfaces are being used in practice by other software developers.
In this paper, we have proposed a novel approach to making this sort of information accessible to package developers by automating the dependency collection and mining of usage samples from every dependency.
We have identified two kinds of rich data sources for collecting downstream dependencies efficiently: public package repositories, such as npm, and online code search engines for finding dependent repositories by their package manifest files, namely Sourcegraph.
We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis beforehand.
We have demonstrated the fundamental usability of our approach with a tool that embeds the downstream dependency data into the Visual Studio Code IDE.

@@

In a wider perspective, we envision many other purposes for analyzing the collected downstream dependency data.
By deriving usage patterns from the samples using an approach such as \cite{zhong2009mapo}, the structure and classification of raw data could be refined.
The derived patterns could also be exploited as suggestions for convenience protocols to package developers.
There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package as per LCOM \citep{chidamber1994metrics}), or that could be attributed to ranges of packages for comparing them with regard to their dependency-based cohesion or their spreading in an ecosystem.

>>>>

Downstream dependencies provide a promising perspective for package developers that are interested in understanding how their interfaces are being used in practice by other software developers.
In this paper, we have proposed a novel approach to making this sort of information accessible to package developers by automating the dependency collection and mining of usage samples from every dependency.
We have identified two kinds of rich data sources for collecting downstream dependencies efficiently: public package repositories, such as npm, and online code search engines for finding dependent repositories by their package manifest files, namely Sourcegraph.
We accomplish the usage mining by scanning the ASTs of every dependency for certain usage patterns that refer to a type from the target package; if the dependency uses a dynamically typed language, we perform a type analysis before.
We have demonstrated the fundamental usability of our approach with a tool that embeds the downstream dependency data into the VS Code IDE.

@@

In a wider perspective, we envision many other purposes for analyzing the collected downstream dependency data.
By deriving usage patterns from the samples using an approach such as \cite{zhong2009mapo}, the structure and classification of raw data could be refined.
The derived patterns could also be exploited as suggestions for convenience protocols to package developers.
There are many ways to turn dependency data into metrics that either could be used for classifying downstream dependencies (e.g., according to their coupling to the target package as per LCOM \citep{chidamber1994metrics}), or that could be attributed to ranges of packages for comparing them concerning their dependency-based cohesion or their spreading in an ecosystem.
